Describing the scale and composition of police demand in Detroit.

### 2021-08-23 paper.Rmd
prop graphic labels

\begin{landscape}

```{r fig1, fig.align = "center", fig.cap = "Proportional breakdown of deployed time spent on each incident category."}
knitr::include_graphics("visuals/fig1_time_ann.png")
```

\end{landscape}

@@

```{r fig2, fig.align = "center", fig.cap = "Mean incident counts by day and week by demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig2_time_heat.png")
```

```{r fig3, fig.align = "center", fig.cap = "Spatial patterning of total incident counts by demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig3_maps.png")
```

>>>>

<!-- \begin{landscape} -->

```{r fig1, fig.align = "center", fig.cap = "Proportional breakdown of deployed time spent on each incident category.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig1_time_port.png")
```

<!-- \end{landscape} -->

@@

```{r fig2, fig.align = "center", fig.cap = "Mean incident counts by day and week, for each demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig2_time_heat.png")
```

```{r fig3, fig.align = "center", fig.cap = "Spatial patterning of total incident counts for each demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig3_maps.png")
```
